#Assignment 2
  A (max) 2,000 word proposal created with R Markdown.
The proposal will:
* Be written in R Markdown.
* State your research question. And justify why it is interesting.
* Provide a basic literature review (properly cited with BibTeX).
* Identify data sources and appropriate research methodologies for answering your question.

##Research Question
  Our researching question is based on whether the Internet accesibility rate has a direct impact on the students academic ability and the economic growth. Currently, it can be argued that not having a proper Internet accessibility can decrease the potencial of the students when learning. Moreover, this can also be harmful for the GDP growth, because future generations will not be prepared to apply new technologies and, therefore, losing the chance to apply one of the most efficient methods to produce benefits.

##Hypothesis
  Our hypothesis is that Internet accessibility is beneficial for both student's academic record and economic growth.

##Data Sources and Methodologie
  We will refer "World DataBank"" and Central Intelligence agency(CIA)'s "Factbook" and  use datas as follows:
* Internet Users (CIA)
https://www.cia.gov/library/publications/resources/the-world-factbook/fields/2153.html#xx

Likewise, we also will use the QOG dataset 2016. A recopilation of data made by the University of Gothenburg. We will use data on education and internet infrastructure.
QOG Data: http://qog.pol.gu.se/data/datadownloads/qogstandarddata





```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
